---
title: "MAS-Thesis-SMM-and-Trend-Monitoring-Sentiment-Analysis"
author: "ajpucher"
date: "2018 M08 5"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Inventory of all libs / load all libs here

```{r}
library(ggplot2)
library(twitteR)
library(reshape2)
library(dplyr)
library(magrittr)
library(tidytext)
library(ggrepel)



```

### Source / load necessary R functions

```{r}
# Current working dir
getwd()

# Load authentication functions
source("../functions/auth.R")
# Load utils
source("../functions/util.R")

```

### Authentication to Twitter API (works, July 2018)

```{r}
# Start Authentication to Twitter API
auth_twitter()

```

### Starting sentiment analysis, first examples
```{r}

load('../../data/output/smm-banks-fintech-output-descr-ratio-melted.Rdata')
options(scipen=999)  # turn-off scientific notation like 1e+48

#Some examples

#Trends in ZRH, Switzerland
#return data frame with name, country & woeid. 
Locs <- availableTrendLocations()
# Where woeid is a numerical identification code describing a location ID
# Filter the data frame for Delhi (India) and extract the woeid of the same
LocsCH = subset(Locs, country == "Switzerland") 
woeidZurich = subset(LocsCH, name == "Zurich")$woeid
# getTrends takes a specified woeid and returns the trending topics associated with that woeid
trends = getTrends(woeid=woeidZurich)
trends

# Search tweets about "Swiss Bank in a specific time range"
head(searchTwitter('Swiss Bank', since='2015-08-01', until= '2018-08-05'))

# Search for ubsschweiz tweets
ubsschweiz_tweets <- searchTwitter("ubsschweiz", n=500, lang="de")
zkbch_tweets <- searchTwitter("zkb_ch", n=500, lang="de")
str(ubsschweiz_tweets)

```


### Starting sentiment analysis with loading data from fintech sector, using tidytext, lang=en
```{r}
# Load again initial file (before norm and ratio calculations)
load('../../data/output/smm-banks-fintech-output-descriptives.Rdata')
options(scipen=999)  # turn-off scientific notation like 1e+48

d.file

# Filter type "Fintech"
df_sa_fintech <- filter(d.file, type == "Fintech")
df_sa_fintech


# Subselect account name for Twitter search "tw_parse"
df_sub_sa_ft <- subset(df_sa_fintech, select=c("tw_parse"))
df_sub_sa_ft <- na.omit(df_sub_sa_ft)


# Create list of dataframes of each account - FINTECH
fintech_list = list()

for (i in 1:nrow(df_sub_sa_ft)) {
  print (i)
  
  tweets <- searchTwitter(df_sub_sa_ft$tw_parse[i], n=500, lang="en")
  
  if (length(tweets) != 0) {
    tweetsDF <- twListToDF(tweets) # Convert to DF
    tweetsDF$tw_parse <- df_sub_sa_ft$tw_parse[i] # Keep track from which account parsed
    fintech_list[[i]] <- tweetsDF # Add it to your list
  }
  
}

# Bind rows - final data
fintech_data_all_tweets <- dplyr::bind_rows(fintech_list)
# Save
save(fintech_data_all_tweets, file = '../../data/output/smm-banks-fintech-output-fintech-data-all-tweets.Rdata')

fintech_data_all_tweets

```


```{r}

df_sa_banks <- filter(d.file, type == "Bank")
df_sa_banks

df_sub_sa_banks <- subset(df_sa_banks, select=c("tw_parse"))
df_sub_sa_banks <- na.omit(df_sub_sa_banks)

# Create list of dataframes of each account - BANKS
banks_list = list()

for (i in 1:nrow(df_sub_sa_banks)) {
  print (i)
  
  tweets <- searchTwitter(df_sub_sa_banks$tw_parse[i], n=500, lang="de")
  
  if (length(tweets) != 0) {
    tweetsDF <- twListToDF(tweets) # Convert to DF
    tweetsDF$tw_parse <- df_sub_sa_banks$tw_parse[i] # Keep track from which account parsed
    banks_list[[i]] <- tweetsDF # Add it to your list
  }
  
}

# Bind rows - final data
banks_data_all_tweets <- dplyr::bind_rows(banks_list)
# Save
save(banks_data_all_tweets, file = '../../data/output/smm-banks-fintech-output-banks-data-all-tweets.Rdata')

banks_data_all_tweets


```

### Cleaning fintech data
### see also https://www.datacamp.com/community/tutorials/sentiment-analysis-R
```{r}
# Load data
load('../../data/output/smm-banks-fintech-output-fintech-data-all-tweets.Rdata')

glimpse(fintech_data_all_tweets)

#Created in the first tutorial
undesirable_words <- c(" ai ", " ca ", " la ", "hey", " na ", " da ", " uh ", " tin ", "  ll",  "la", "da", "uh", "ah")

#Create tidy text format: Unnested, Unsummarized, -Undesirables, Stop and Short words
ft_data_tidy <- fintech_data_all_tweets %>%
  unnest_tokens(word, text) %>% #Break the text into individual words
  filter(!word %in% undesirable_words) %>% #Remove undesirables
  filter(!nchar(word) < 3) %>% #Words like "ah" or "oo"
  anti_join(stop_words) #Data provided by the tidytext package

glimpse(ft_data_tidy)

```

### Create sentiment datasets (bing, nrc, nrc polarity, afinn)
### see also https://www.datacamp.com/community/tutorials/sentiment-analysis-R
```{r}
ft_data_bing <- ft_data_tidy %>%
  inner_join(get_sentiments("bing"))

ft_data_nrc <- ft_data_tidy %>%
  inner_join(get_sentiments("nrc"))

ft_data_nrc_sub <- ft_data_tidy %>%
  inner_join(get_sentiments("nrc")) %>%
  filter(!sentiment %in% c("positive", "negative"))

ft_data_afinn <- ft_data_tidy %>%
  inner_join(get_sentiments("afinn"))

```

### Plotting first sentiment analysis results
### see also https://www.datacamp.com/community/tutorials/sentiment-analysis-R
```{r}

# Plotting word count
nrc_plot <- ft_data_nrc %>%
  group_by(sentiment) %>%
  summarise(word_count = n()) %>%
  ungroup() %>%
  mutate(sentiment = reorder(sentiment, word_count)) %>%
  #Use `fill = -word_count` to make the larger bars darker
  ggplot(aes(sentiment, word_count, fill = -word_count)) +
  geom_col() +
  guides(fill = FALSE) + #Turn off the legend
  labs(x = NULL, y = "Word Count") +
  scale_y_continuous(limits = c(0, 3000)) + #Hard code the axis limit
  ggtitle("Entity Type Fintech: Word Count - NRC Sentiment") +
  coord_flip()
nrc_plot

ggsave("../../img/charts-sent-analysis/chart1_s-a-nrc-word-count.png")

# Plotting NRC sentiments with words, which triggered those sentiments
plot_words <- ft_data_nrc %>%
  group_by(sentiment) %>%
  count(word, sort = TRUE) %>%
  arrange(desc(n)) %>%
  slice(seq_len(8)) %>% #consider top_n() from dplyr also
  ungroup()

plot_words %>%
  #Set `y = 1` to just plot one variable and use word as the label
  ggplot(aes(word, 1, label = word, fill = sentiment )) +
  #You want the words, not the points
  geom_point(color = "transparent") +
  #Make sure the labels don't overlap
  geom_label_repel(force = 1,nudge_y = .5,  
                   direction = "y",
                   box.padding = 0.04,
                   segment.color = "transparent",
                   size = 3) +
  facet_grid(~sentiment) +
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.title.x = element_text(size = 6),
        panel.grid = element_blank(), panel.background = element_blank(),
        panel.border = element_rect("lightgray", fill = NA),
        strip.text.x = element_text(size = 9)) +
  xlab(NULL) + ylab(NULL) +
  ggtitle("Entity Type Fintech: Trigger Words - NRC Sentiment") +
  coord_flip()

ggsave("../../img/charts-sent-analysis/chart2_s-a-nrc-words-sentiments.png")

# Plotting AFINN histogram
ggplot(data=ft_data_afinn, aes(x=ft_data_afinn$score)) + 
  geom_histogram(breaks=seq(-10, 10, by=1), 
                 col="black", 
                 fill="blue", 
                 alpha = .2) + 
  labs(title="Entity Type Fintech: Histogram AFINN Senti-Score", x="Score", y="Frequency")

ggsave("../../img/charts-sent-analysis/chart3_s-a-afinn-hist-senti-score.png")

# SD, Mean, Median
ft_hist_afinn <- c(sd(ft_data_afinn$score), mean(ft_data_afinn$score), median(ft_data_afinn$score))
ft_hist_afinn


```
