---
title: "MAS-Thesis-SMM-and-Trend-Monitoring-Descriptives"
author: "ajpucher"
date: "2018 M07 4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Inventory of all libs / load all libs here

```{r}
library(ggplot2)
library(twitteR)
library(reshape2)
library(dplyr)
library(forcats)

# Inactive
# library(Rlinkedin)

```

### Source / load necessary R functions

```{r}
# Current working dir
getwd()

# Load authentication functions
source("../functions/auth.R")
# Load utils
source("../functions/util.R")



```


### Authentication to Twitter API (works, July 2018)
### Authentication to LinkedIn API (works, July 2018)
### Authentication to FB API: This is unfortunately not supported anymore! Check: http://theconversation.com/facebooks-data-lockdown-is-a-disaster-for-academic-researchers-94533

```{r}
# Start Authentication to Twitter API
auth_twitter()

#Start Authentication to LinkedIn API
in.auth <- auth_linkedin()

```

### Read the input dataset gathered by research

```{r}
getwd()

# Read csv, use ANSI encoding
d.file <- read.csv("../../data/input/smm-banks-fintech-input-dataset.csv", sep=";", head=TRUE, stringsAsFactors=FALSE, encoding = "ANSI")
head(d.file)
dim(d.file)

d.file

```

### Show some plots and descriptive statistics

```{r}

# Show type (bank or fintech) compared to funding year
ggplot(d.file, aes(x = year, y = type)) +
  geom_point() +
  xlab("Funding Year") +
  ylab("Type") +
  theme_bw()

# Save to file
ggsave("../../img/charts/chart1_type_fundingyear.png")

```


### Access and query Twitter API - Example user "ETH"

```{r}

#get user "ETH"
user=getUser("ETH")

# User name
user
# User created date
user$created

# User details
# User likes (favorites)
user$favoritesCount
# Follower
user$followersCount
# User follows (friends)
user$friendsCount
# User tweets
user$statusesCount

```


### Access and query LinkedIn API - Example user "LinkedIn"
### Only basic profile metadata available, for everything else you need to be a member of the Partnership Program...

```{r}
search.comp <- searchCompanies(in.auth, keywords = "LinkedIn")
head(search.comp)

getProfile(token = in.auth, connections = FALSE, id = NULL)

#does not work - restricted
my.groups <- getGroups(token = in.auth, details=TRUE)
#does not work - restricted
search.results <- searchJobs(token = in.auth, keywords = "data scientist")


```



### Use the input datafile, read and add all Twitter metadata to the given accounts, and write everything to an output file, for further analysis and descriptive statistics.

```{r}
# Show file
(d.file)

# Count rows of file
nrow(d.file)

# Add all Twitter metadata to the dataset
for (i in 1:nrow(d.file)) {

  # Skip an API request if value is NA, go to next iteration
  if(is.na(d.file[i, 'tw_parse'])) next

  user = getUser(d.file[i, 'tw_parse'])
  
  d.file[i,'tw_favorites'] <- user$favoritesCount
  d.file[i,'tw_followers'] <- user$followersCount
  d.file[i,'tw_friends']   <- user$friendsCount
  d.file[i,'tw_statuses']  <- user$statusesCount
  
}

# Save and write as Rdata file to output directory
save(d.file, file = '../../data/output/smm-banks-fintech-output-descriptives.Rdata')

```

### Load data file
```{r}

# Load the saved file (we don´t have to go through the whole process above again)
load('../../data/output/smm-banks-fintech-output-descriptives.Rdata')
d.file
d.cleanfile <- (na.omit(d.file))

nrow(d.cleanfile)
str(d.cleanfile)

d.cleanfile
```


### EDA: Some first explorative data analysis, show some descriptive statistics and plots (not normalized)
```{r}
# Chart: Tw followers vs. Fb followers
ggplot(d.cleanfile, aes(x=tw_followers, y=fb_followers)) +
  geom_point(aes(color=as.factor(type))) +
  labs(x = "Twitter followers", y = "Facebook followers")+
  scale_color_discrete(name=("Type"))+
  ylim(c(0,4500))+
  xlim(c(0,2600))

ggsave("../../img/charts/chart2_twfollowers_fbfollowers.png")

# Chart: Tw favorites vs. Fb favorites
ggplot(d.cleanfile, aes(x=tw_favorites, y=fb_favorites)) +
  geom_point(aes(color=as.factor(type))) +
  labs(x = "Twitter favorites", y = "Facebook favorites")+
  scale_color_discrete(name=("Type"))+
  ylim(c(0,5000))+
  xlim(c(0,2000))

ggsave("../../img/charts/chart3_twfavorites_fbfavorites.png")

# Chart: Boxplot Tw followers
ggplot(d.cleanfile) +
  geom_boxplot(aes(type, tw_followers),color="black") +
  labs(x = "Type", y = "Twitter followers")+
  ylim(c(0,10000))

ggsave("../../img/charts/chart4_boxplot_twfollowers.png")

# Chart: Fb favorites vs. employees
ggplot(d.cleanfile, aes(x=employees, y=fb_favorites)) +
  geom_point(aes(color=as.factor(type))) +
  labs(x = "Employees", y = "Facebook favorites")+
  scale_color_discrete(name=("Type"))+
  ylim(c(0,6000))+
  xlim(c(0,2000))

ggsave("../../img/charts/chart5_employees_fb_favorites.png")


# Chart: Fb followers vs. employees
ggplot(d.cleanfile, aes(x=employees, y=fb_followers)) +
  geom_point(aes(color=as.factor(type))) +
  labs(x = "Employees", y = "Facebook followers")+
  scale_color_discrete(name=("Type"))+
  ylim(c(0,6000))+
  xlim(c(0,2000))

ggsave("../../img/charts/chart6_employees_fb_followers.png")


# Chart: Tw followers vs. employees
ggplot(d.cleanfile, aes(x=employees, y=tw_followers)) +
  geom_point(aes(color=as.factor(type))) +
  labs(x = "Employees", y = "Twitter followers")+
  scale_color_discrete(name=("Type"))+
  ylim(c(0,6000))+
  xlim(c(0,2000))

ggsave("../../img/charts/chart7_employees_tw_followers.png")


# Chart: Tweets vs. employees
ggplot(d.cleanfile, aes(x=employees, y=tw_statuses)) +
  geom_point(aes(color=as.factor(type))) +
  labs(x = "Employees", y = "Tweets")+
  scale_color_discrete(name=("Type"))+
  ylim(c(0,10000))+
  xlim(c(0,10000))

ggsave("../../img/charts/chart8_employees_tw_statuses.png")



```


### Load data file, convert it to dataframe, normalize values with z standardization and calc. employee to tw / fb numbers as percentage / ratio
```{r}

# Load the saved file (we don´t have to go through the whole process from above again)
load('../../data/output/smm-banks-fintech-output-descriptives.Rdata')
d.file
df <- as.data.frame(d.file)

# Do normalization - Z standardization
dfNormZ <- as.data.frame(scale(d.file[,c("employees", "tw_favorites", "tw_followers", "tw_friends", "tw_statuses", "fb_favorites", "fb_followers")]))

# Add new values as columns to the dataframe df
df$normz_employees = dfNormZ$employees
df$normz_tw_favorites = dfNormZ$tw_favorites
df$normz_tw_followers = dfNormZ$tw_followers
df$normz_tw_friends = dfNormZ$tw_friends
df$normz_tw_statuses = dfNormZ$tw_statuses
df$normz_fb_favorites = dfNormZ$fb_favorites
df$normz_fb_followers = dfNormZ$fb_followers

# Calculate employee and tw / fb numbers as percentage / ratio
df$ratio_tw_favorites = df$tw_favorites/df$employees*100
df$ratio_tw_followers = df$tw_followers/df$employees*100
df$ratio_tw_friends = df$tw_friends/df$employees*100
df$ratio_tw_statuses = df$tw_statuses/df$employees*100
df$ratio_fb_favorites = df$fb_favorites/df$employees*100
df$ratio_fb_followers = df$fb_followers/df$employees*100

df

# Save and write as Rdata file to output directory
save(df, file = '../../data/output/smm-banks-fintech-output-descr-znorm-and-ratio.Rdata')

```

### Load the saved file (we don´t have to go through the whole process above again)
### Melt data for ggplot2, and filter
```{r}
load('../../data/output/smm-banks-fintech-output-descr-znorm-and-ratio.Rdata')

df

dfm <- melt(data = df, id.vars = c("year", "name", "type", "category", "place", "canton", "employees"), 
            measure.vars = c("tw_favorites", "tw_followers", "tw_friends", "tw_statuses", "fb_favorites", "fb_followers", "normz_employees",
                             "normz_tw_favorites", "normz_tw_followers", "normz_tw_friends", "normz_tw_statuses", "normz_fb_favorites", "normz_fb_followers","ratio_tw_favorites",
                             "ratio_tw_followers", "ratio_tw_friends", "ratio_tw_statuses", "ratio_fb_favorites", "ratio_fb_followers"))

dfm

dfmf_normz <- filter(dfm, variable == "normz_employees" | variable == "normz_tw_favorites" | variable == "normz_tw_followers" | variable ==  "normz_tw_friends" | variable == "normz_tw_statuses" | variable ==  "normz_fb_favorites" | variable ==  "normz_fb_followers" )

dfmf_ratio <- filter(dfm, variable == "ratio_tw_favorites" | variable == "ratio_tw_followers" | variable == "ratio_tw_friends" | variable == "ratio_tw_statuses" | variable == "ratio_fb_favorites" | variable == "ratio_fb_followers")

dfmf_normz
dfmf_ratio

```

### Descriptive Stats: SMA (Social Media Activity) Ratio Plots
```{r}

options(scipen=999)  # turn-off scientific notation like 1e+48

# Create labels for charts
SocMedActLabs <- c("TW Favorites", "TW Followers", "TW Friends", "TW Statuses", "FB Favorites", "FB Followers")

# Chart: Social Media Activity Type (SMAT) Compared to Social Media Activity Ratio (SMAR)
ggplot(dfmf_ratio, aes(x=(variable), y=log10(value)) ) + 
  geom_point(aes(col=as.factor(type), size=employees)) + 
  labs(y="SMAR (log10 scale)", 
       x="SMAT", 
       title="Social Media Activity Type (SMAT) Compared to Social Media Activity Ratio (SMAR)")+
  scale_color_discrete(name="Entity Type") +
  scale_size_continuous(name="Employee Size")+
  scale_x_discrete(labels=SocMedActLabs)+
  theme(axis.text.x = element_text(angle=45, vjust=0.5, size=10))

ggsave("../../img/charts-ratio/chart1_smat_comp_to_smar.png")
```


```{r}
# Chart: Boxplot Social Media Activity Ratio (SMAR) Compared to Entity Type Total
ggplot(dfmf_ratio) +
  geom_boxplot(aes(type, log10(value))) +
  labs(x = "Type", y = "SMAR (log10 scale)",
       title="Social Media Activity Ratio (SMAR) Compared to Entity Type Total")

ggsave("../../img/charts-ratio/chart2_smar_comp_to_entity_type_total.png")
```

```{r}
# Chart: Employee size vs. Social Media Activity Total
ggplot(dfmf_ratio, aes(x=log10(employees), y=log10(value)) ) +
  geom_point(aes(col=as.factor(type) )) +
  labs(x = "Employee Size (log10 scale)", y = "SMAR (log10 scale)",
       title="Social Media Activity Ratio (SMAR) Compared to Employee Size Total") +
  scale_color_discrete(name="Entity Type")

ggsave("../../img/charts-ratio/chart3_smar_comp_to_employee_size_total.png")
```

```{r}

dfmf_ratio_sorted <-na.omit(dfmf_ratio)
dfmf_ratio_sorted <-dfmf_ratio_sorted[order(dfmf_ratio_sorted$type, dfmf_ratio_sorted$category, dfmf_ratio_sorted$value),]
dfmf_ratio_sorted

# Chart: Boxplot Social Media Activity Ratio (SMAR) Compared to Entity Category
ggplot(dfmf_ratio_sorted) +
  geom_boxplot(aes(as.factor(category), y=log10(value), col=as.factor(type) ) ) +
  labs(x = "Entity Category", y = "SMAR (log10 scale)",
    title="Social Media Activity Ratio (SMAR) Compared to Entity Category Total")+
  scale_color_discrete(name="Entity Type")+
  coord_flip()

ggsave("../../img/charts-ratio/chart4_smar_comp_to_entity_category.png")

```