---
title: "MAS-Thesis-SMM-and-Trend-Monitoring-Descriptives"
author: "ajpucher"
date: "2018 M07 4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Inventory of all libs / load all libs here

```{r}
library(ggplot2)
library(twitteR)
library(Rlinkedin)


```

### Source / load necessary R functions

```{r}
# Current working dir
getwd()

# Load authentication functions
source("../functions/auth.R")



```


### Authentication to Twitter API (works, July 2018)
### Authentication to LinkedIn API (works, July 2018)
### Authentication to FB API: This is unfortunately not supported anymore! Check: http://theconversation.com/facebooks-data-lockdown-is-a-disaster-for-academic-researchers-94533

```{r}
# Start Authentication to Twitter API
auth_twitter()

#Start Authentication to LinkedIn API
in.auth <- auth_linkedin()

```

### Read the input dataset gathered by research

```{r}
getwd()

# Read csv, use ANSI encoding
d.file <- read.csv("../../data/input/smm-banks-fintech-input-dataset.csv", sep=";", head=TRUE, stringsAsFactors=FALSE, encoding = "ANSI")
head(d.file)
dim(d.file)

d.file

```

### Show some plots and descriptive statistics

```{r}

# Show type (bank or fintech) compared to funding year
ggplot(d.file, aes(x = year, y = type)) +
  geom_point() +
  xlab("Funding Year") +
  ylab("Type") +
  theme_bw()

# Save to file
ggsave("../../img/charts/chart1_type_fundingyear.png")

```


### Access and query Twitter API - Example user "ETH"

```{r}

#get user "ETH"
user=getUser("ETH")

# User name
user
# User created date
user$created

# User details
# User likes (favorites)
user$favoritesCount
# Follower
user$followersCount
# User follows (friends)
user$friendsCount
# User tweets
user$statusesCount

```


### Access and query LinkedIn API - Example user "LinkedIn"
### Only basic profile metadata available, for everything else you need to be a member of the Partnership Program...

```{r}
search.comp <- searchCompanies(in.auth, keywords = "LinkedIn")
head(search.comp)

getProfile(token = in.auth, connections = FALSE, id = NULL)

#does not work - restricted
my.groups <- getGroups(token = in.auth, details=TRUE)
#does not work - restricted
search.results <- searchJobs(token = in.auth, keywords = "data scientist")


```



### Use the input datafile, read and add all Twitter metadata to the given accounts, and write everything to an output file, for further analysis and descriptive statistics.

```{r}
# Show file
(d.file)

# Count rows of file
nrow(d.file)

# Add all Twitter metadata to the dataset
for (i in 1:nrow(d.file)) {

  # Skip an API request if value is NA, go to next iteration
  if(is.na(d.file[i, 'tw_parse'])) next

  user = getUser(d.file[i, 'tw_parse'])
  
  d.file[i,'tw_favorites'] <- user$favoritesCount
  d.file[i,'tw_followers'] <- user$followersCount
  d.file[i,'tw_friends']   <- user$friendsCount
  d.file[i,'tw_statuses']  <- user$statusesCount
  
}

# Save and write as Rdata file to output directory
save(d.file, file = '../../data/output/smm-banks-fintech-output-descriptives.Rdata')

```

### Load data file
```{r}

# Load the saved file (we don´t have to go through the whole process above again)
load('../../data/output/smm-banks-fintech-output-descriptives.Rdata')
d.file
d.cleanfile <- (na.omit(d.file))

nrow(d.cleanfile)
str(d.cleanfile)

d.cleanfile
```


### Show some descriptive statistics and plots (not normalized)
```{r}
# Chart: Tw followers vs. Fb followers
ggplot(d.cleanfile, aes(x=tw_followers, y=fb_followers)) +
  geom_point(aes(color=as.factor(type))) +
  labs(x = "Twitter followers", y = "Facebook followers")+
  scale_color_discrete(name=("Type"))+
  ylim(c(0,4500))+
  xlim(c(0,2600))

ggsave("../../img/charts/chart2_twfollowers_fbfollowers.png")

# Chart: Tw favorites vs. Fb favorites
ggplot(d.cleanfile, aes(x=tw_favorites, y=fb_favorites)) +
  geom_point(aes(color=as.factor(type))) +
  labs(x = "Twitter favorites", y = "Facebook favorites")+
  scale_color_discrete(name=("Type"))+
  ylim(c(0,5000))+
  xlim(c(0,2000))

ggsave("../../img/charts/chart3_twfavorites_fbfavorites.png")

# Chart: Boxplot Tw followers
ggplot(d.cleanfile) +
  geom_boxplot(aes(type, tw_followers),color="black") +
  labs(x = "Type", y = "Twitter followers")+
  ylim(c(0,10000))

ggsave("../../img/charts/chart4_boxplot_twfollowers.png")

# Chart: Fb favorites vs. employees
ggplot(d.cleanfile, aes(x=employees, y=fb_favorites)) +
  geom_point(aes(color=as.factor(type))) +
  labs(x = "Employees", y = "Facebook favorites")+
  scale_color_discrete(name=("Type"))+
  ylim(c(0,6000))+
  xlim(c(0,2000))

ggsave("../../img/charts/chart5_employees_fb_favorites.png")


# Chart: Fb followers vs. employees
ggplot(d.cleanfile, aes(x=employees, y=fb_followers)) +
  geom_point(aes(color=as.factor(type))) +
  labs(x = "Employees", y = "Facebook followers")+
  scale_color_discrete(name=("Type"))+
  ylim(c(0,6000))+
  xlim(c(0,2000))

ggsave("../../img/charts/chart6_employees_fb_followers.png")


# Chart: Tw followers vs. employees
ggplot(d.cleanfile, aes(x=employees, y=tw_followers)) +
  geom_point(aes(color=as.factor(type))) +
  labs(x = "Employees", y = "Twitter followers")+
  scale_color_discrete(name=("Type"))+
  ylim(c(0,6000))+
  xlim(c(0,2000))

ggsave("../../img/charts/chart7_employees_tw_followers.png")


# Chart: Tweets vs. employees
ggplot(d.cleanfile, aes(x=employees, y=tw_statuses)) +
  geom_point(aes(color=as.factor(type))) +
  labs(x = "Employees", y = "Tweets")+
  scale_color_discrete(name=("Type"))+
  ylim(c(0,10000))+
  xlim(c(0,10000))

ggsave("../../img/charts/chart8_employees_tw_statuses.png")



```


### Load data file, convert it to dataframe
```{r}

# Load the saved file (we don´t have to go through the whole process above again)
load('../../data/output/smm-banks-fintech-output-descriptives.Rdata')
d.file

#dfNormZ <- as.data.frame( scale(df[1:2] ))

df <- as.data.frame(scale(d.file[,c("employees", "tw_favorites", "tw_followers", "tw_friends", "tw_statuses", "fb_favorites", "fb_followers")]))
df




```


